Dear ---,
  

I would like to take this opportunity to invite you on behalf of the HUST-16
organisers to be a member of the program committee for the 3rd International
Workshop on HPC User Support Tools (HUST-16) to be held at Supercomputing 2016
(SC16) in Salt Lake City Utah on 13 November 2016.  This will be a half-day
workshop, during which we would have 5 or 6 paper presentations.  
One of the output goals of the workshop is again to have the accepted papers
published via ACM/IEEE through SIGHPC.  To meet this publication goal, we need
formal approval from SIGHPC and this requires a program committee to be in
place.

We will strictly adhere to the following time line:
- Call for papers issued and submissions open: start of May 2016 pending SIGHPC
  approval
- Submission deadline: 12 August 2016 (optional extension: 19 August 2016)
- Workshop paper reviews: by 29 September 2016
- Final program Committee meeting: last week of September 2016
- Acceptance notifications: 29 Sept 2016
- Camera-ready papers due: 13 October 2016 (Firm deadline for uploading to
  ACM/IEEE is 15 October 2016)

HUST has received 9-10 papers each year and we are anticipating a similiar number of
papers this time. We estimate program committee members will have to
review 3-4 papers.  The submissions and reviews will be done through 
EasyChair using a double blind reviewing process.  Program committee members
will be able to bid for papers after which a definite assignment will be made.
There will be no travel involved for program committee members, meetings will
be held by means of conference call on dates relevant to the time line.  Please
find the workshop proposal attached. Once we have SIGHPC approval, the workshop
webpage (TBA) will have more information.

Please let us know as soon as possible whether or not you would like to accept
our invitation to be a part of the HUST-16 workshop program committee.  Should
you be unable to join the program committee and you know a viable candidate who
would be willing to volunteer for this, please let us know so we can contact
him/her.  Should you have any questions, please do not hesitate to contact us.

Thanks in advance.

Best regards,

Chris Bording
Todd Gamblin
Olli-
